\documentclass[../DoAn.tex]{subfiles}
% tài liệu tham khảo
\begin{document}
\cite{1_JC_Taylor} Jenny C Taylor, Hilary C Martin ``Factors influencing success of clinical genome sequencing across a broad spectrum of disorders``, Nat Genet,  
 2015;47(7):717–726, doi:10.1038/ng.3304 [PubMed: 25985138].

\cite{2_monkol} Lek M, Karczewski KJ, Minikel EV, et al. ``Analysis of protein-coding genetic variation in 60,706 humans``. Nature. 2016;536(7616):285–291.  
 [PubMed:27535533].

\cite{3_Dewey} Dewey FE, et al. ``Clinical interpretation and implications of whole-genome sequencing``. JAMA. 2014;311(10):1035. doi:10.1001/jama.2014.1717 [PubMed: 24618965].

\cite{useML} Yujia Bao, Zhengyi Deng, Yan Wang, Heeyoon Kim, Victor Diego Armengol, Francisco Acevedo, Nofal Ouardaoui, Cathy Wang, Giovanni Parmigiani, Regina Barzilay, Danielle Braun, and Kevin S. Hughes. ``Using Machine Learning and Natural Language Processing to Review and Classify the Medical Literature on Cancer Susceptibility Genes``. JCO Clinical Cancer Informatics 2019 :3, 1-9.

\cite{GAPscreener} Yu, Wei & Clyne, Mindy & Dolan, Siobhan & Yesupriya, Ajay & Wulf, Anja & Liu, Tiebin & Khoury, Muin & Gwinn, Marta. (2008). GAPscreener: An automatic tool for screening human genetic association literature in PubMed using the support vector machine technique. BMC bioinformatics. 9. 205. 10.1186/1471-2105-9-205. 

\cite{huge} Wei Yu, Marta Gwinn, Melinda Clyne, Ajay Yesupriya, Muin J Khoury. ``A navigator for human genome epidemiology``. Nat Genet. 2008. doi: 10.1038/ng0208-124.

\cite{deng2009imagenet} Deng, Jia and Dong, Wei and Socher, Richard and Li, Li-Jia and Li, Kai and Fei-Fei, Li, ``Imagenet: A large-scale hierarchical image database" 2009 IEEE conference on computer vision and pattern recognition, pp. 248-255, 2009.

\cite{lin2014microsoft} Tsung-Yi Lin , ``Microsoft COCO: Common Objects in Context", 
 arXiv:1405.0312v3, 2014.

\cite{1467360} N. Dalal and B. Triggs, ``Histograms of oriented gradients for human detection,`` 2005 IEEE Computer Society Conference on Computer Vision and Pattern Recognition (CVPR'05), 2005, pp. 886-893 vol. 1, doi: 10.1109/CVPR.2005.177.

\cite{sift} Lindeberg, Tony. ``Scale Invariant Feature Transform``. 2012.  
 10.4249/scholarpedia.10491. 

\cite{HGMD} The Human Gene Mutation Database at the Institute of Medical Genetics in Cardiff (HGMD). ``https://www.hgmd.cf.ac.uk/ac/index.php``. Visited January 26, 2022.

\cite{salton1975vector} Gerard Salton, Anita Wong, and Chung-Shu Yang. ``A vector space model for automatic indexing``. Communications of the ACM, 18(11):613–620, 1975.

\cite{poppler} Python Poppler``https://cbrunet.net/python-poppler/``. Visited April 15, 2022.

\cite{HGVS} HGVS nomenclature standard. ``https://varnomen.hgvs.org/bg-material/simple/`` Visited July 26, 2022.

\cite{PMCtextmining} Donald C Comeau, Chih-Hsuan Wei, ``PMC text mining subset in BioC: about three million full-text articles and growing, Bioinformatics``. Volume 35, Issue 18, 15 September 2019, Pages 3533–3535.``https://doi.org/10.1093/bioinformatics/btz070``.

\cite{PubTator} Chih-Hsuan Wei, Alexis Allot, Robert Leaman, Zhiyong Lu. ``PubTator central: automated concept annotation for biomedical full text articles``. Nucleic Acids Research, Volume 47, Issue W1, 02 July 2019, Pages W587–W593.
 https://doi.org/10.1093/nar/gkz389. 

% \cite{avada} Birgmeier J, Deisseroth CA, Hayward LE, Galhardo LMT, Tierno AP, Jagadeesh KA, Stenson PD, Cooper DN, Bernstein JA, Haeussler M, Bejerano G. AVADA: toward automated pathogenic variant evidence retrieval directly from the full-text literature. Genet Med. 2020 Feb;22(2):362-370. doi: 10.1038/s41436-019-0643-6. Epub 2019 Aug 30. PMID: 31467448; PMCID: PMC7301356.

% \cite{Mastermind} Chunn LM, Nefcy DC, Scouten RW, Tarpey RP, Chauhan G, Lim MS, Elenitoba-Johnson KSJ, Schwartz SA, Kiel MJ. Mastermind: A Comprehensive Genomic Association Search Engine for Empirical Evidence Curation and Genetic Variant Interpretation. Front Genet. 2020 Nov 13;11:577152. doi: 10.3389/fgene.2020.577152. PMID: 33281875; PMCID: PMC7691534.

% \cite{textmining} Singhal A, Simmons M, Lu Z. Text Mining Genotype-Phenotype Relationships from Biomedical Literature for Database Curation and Precision Medicine. PLoS Comput Biol. 2016 Nov 30;12(11):e1005017. doi: 10.1371/journal.pcbi.1005017. PMID: 27902695; PMCID: PMC5130168.

\cite{pubmed} National library of medicine - National center for biotechnology informationional (pubmed). ``https://pubmed.ncbi.nlm.nih.gov/``. Visited July 26, 2022.

\cite{pubMunch} pubMunch3 ``https://github.com/maximilianh/pubMunch3`` Visited April 24, 2022.

\end{document}
